---
title: U.S. Recessions and Covington
author: ''
date: '2023-02-07'
slug: []
categories: []
tags:
  - Development
  - Administration
type: ''
subtitle: 'Covington Unemployment Rate: 1990-2022'
image: ''
---

There have been four economic recessions in the United States since the early 1990s.  A recession is a significant, widespread, and prolonged downturn in economic activity, and is typically identified by two consecutive quarters of negative gross domestic product (GDP) growth.^[https://www.investopedia.com/terms/r/recession.asp]  One of the most noticeable effects of a recession is a rise in unemployment, which usually peaks long after the recession has begun and can last well into recovery.^[https://www.investopedia.com/ask/answers/032515/why-does-unemployment-tend-rise-during-recession.asp] Below is a brief description of the four recessions and the unemployment rate in Covington through these periods.  *Attention is not given to the underlying causes of each recession.*

*   **Early 1990s:** Lasted eight months from July, 1990 - March, 1991. The unemployment rate hovered around 4 percent in the early 1990s prior to the recession, rising to 6 percent at the end of the recession, and peaked at nearly 9 percent over a year later.

*   **Early 2000s:** Lasted eight months from March, 2001 - November, 2001.  In Covington, the rise in the unemployment rate was not as steep as during the early 1990s, with unemployment remaining between 5-6 percent during most of the 2000s. 

*   **Great Recession:** Lasted one year and six months from December 2007 - June 2009.   Unemployment in Covington increased dramatically over the recession period, rising from 5 percent in December, 2007 to 11.8 percent in June, 2009. Eight months  later in February, 2010 unemployment peaked at 12. 5 percent.

*   **COVID-19:** Lasted two months from February, 2020 - April, 2020.  The recession was short, but the effect on employment was quick and severe.  Nationwide, more than 24 million people lost their jobs in April 2020 ^[https://www.nytimes.com/2020/04/09/business/economy/unemployment-claim-numbers-coronavirus.html].  In Kenton County, KY (Covington is within Kenton County) unemployment insurance claims rose from 67 to 2,683 over the month of March, 2020.^[https://kystats.ky.gov/KYLMI/UnemploymentClaimsData]  Consequently, unemployment in Covington was at 15.6 percent by April, 2020.  As of December, 2022 unemployment in Covington is 3.4 percent.

The graph below displays the above four recession periods and the unemployment rate in Covington since 1990.

 

```{r setup, include=FALSE, echo = FALSE}

library(tidyverse)
library(lubridate)
library(ggpubr)
library(knitr)
library(magick)
library(showtext)
library(extrafont)
library(scales)
library(png)
library(cowplot)
library(grid)
theme_set(theme_pubr())
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)


source("covdata_graphics.r")

#Load Data
unmp_rate <- readRDS("unmp_rate.rds")

unmp_rate <- unmp_rate %>%
  filter(Value <= 20 & Group != "Kenton Co." & Group != "Kentucky")%>%#removes rows that are not percents with decimal
  transmute(Date = lubridate::ym(Label), Rate = Value, Group = Group)%>%
  mutate(Date = format(strptime(Date, 
                                format='%Y-%m-%d'), '%Y-%m'))

```




```{r eval=TRUE}


#specifying labels  
plot_labels <-  labs(x = "Month/Year", 
       y = "Incentives\n", 
       title = "U.S. Recessions and Covington",
       subtitle = "Covington Unemployment Rate: 1990-2022\n",
       caption = "Administration\nCity of Covington\nSource: BLS | CovData | 2023")
  

#unemployment rate by month and year
unemployment_plot <- unmp_rate %>%
  mutate_at(vars(Date), list(ym))%>%
  mutate(`M-Y` = format(Date, "%m-%Y"))%>%
  ggplot(aes(x=Date, y=Rate, label = `M-Y`))+
  geom_rect(aes(xmin = ym("1990-07"), xmax = ym("1991-03"), 
                ymin = -Inf, ymax = Inf), alpha = 0.01, fill = "#00c1de", colour = NA)+
  geom_rect(aes(xmin = ym("2001-03"), xmax = ym("2001-11"), 
                ymin = -Inf, ymax = Inf), alpha = 0.01, fill = "#00c1de", colour = NA)+
  geom_rect(aes(xmin = ym("2007-12"), xmax = ym("2009-06"), 
                ymin = -Inf, ymax = Inf), alpha = 0.01, fill = "#00c1de", colour = NA)+
  geom_rect(aes(xmin = ym("2020-02"), xmax = ym("2020-04"), 
                ymin = -Inf, ymax = Inf), alpha = 0.01, fill = "#00c1de", colour = NA)+
  geom_label(aes(x = ym("1991-06"), y = 14, label = "Early 1990s"), 
             hjust = 0, 
             vjust = 0.5, 
             lineheight = 0.8,
             colour = "black", 
             fill = "#cccccc", 
             label.size = NA, 
             family="Franklin Gothic Medium", 
             size = 3) +
  geom_curve(aes(x = ym("1994-06"), y = 13, xend = ym("1991-04"), yend = 12), 
                           colour = "#555555", 
                           curvature = -0.3,
                           size=0.5,
                          arrow = arrow(length = unit(0.03, "npc")))+
   geom_label(aes(x = ym("1996-06"), y = 10, label = "Early 2000s"), 
             hjust = 0, 
             vjust = 0.5, 
             lineheight = 0.8,
             colour = "black", 
             fill = "#cccccc", 
             label.size = NA, 
             family="Franklin Gothic Medium", 
             size = 3) +
  geom_curve(aes(x = ym("1999-06"), y = 9, xend = ym("2000-12"), yend = 8), 
                           colour = "#555555", 
                           curvature = 0.2,
                           size=0.5,
                          arrow = arrow(length = unit(0.03, "npc")))+
   geom_label(aes(x = ym("2002-09"), y = 12, label = "Great\nRecession"), 
             hjust = 0, 
             vjust = 0.5, 
             lineheight = 0.8,
             colour = "black", 
             fill = "#cccccc", 
             label.size = NA, 
             family="Franklin Gothic Medium", 
             size = 3) +
  geom_curve(aes(x = ym("2005-06"), y = 11, xend = ym("2007-06"), yend = 9), 
                           colour = "#555555", 
                           curvature = 0.2,
                           size=0.5,
                          arrow = arrow(length = unit(0.03, "npc")))+
  geom_label(aes(x = ym("2015-01"), y = 14, label = "COVID-19"), 
             hjust = 0, 
             vjust = 0.5, 
             lineheight = 0.8,
             colour = "black", 
             fill = "#cccccc", 
             label.size = NA, 
             family="Franklin Gothic Medium", 
             size = 3) +
  geom_curve(aes(x = ym("2017-01"), y = 13, xend = ym("2020-01"), yend = 12), 
                           colour = "#555555", 
                           curvature = 0.2,
                           size=0.5,
                          arrow = arrow(length = unit(0.03, "npc")))+
  #geom_area(fill = "red")+
  geom_line(lwd = 0.8) + 
  #geom_point(size = 1) +
  scale_x_date(breaks = seq(ym("1990-01"), ym("2022-12"), by = "10 years"), date_labels = "%Y" )+
  plot_labels+
 
  covdata_theme(panel.background.fill = "covington.plain")

covdata_plot(unemployment_plot, "cov.logo.blue")
  

  
  



```