---
title: "Grants for urgent home repairs keep vulnerable Covington families in their homes"
author: ''
date: '2024-09-27'
slug: []
categories: []
tags:
  - Development
type: ''
subtitle: ''
image: ''
---

```{r setup, include=FALSE, echo = FALSE, warning = FALSE, message=FALSE}

library("tidyverse")
library("lubridate")
library("plotly")
library(readxl)
library(covdataplot)
library(magick)
library(extrafont)
library(sf)
library(ggmap)
library(gganimate)
library(gghighlight)
library(scales)
library(tidyquant)
library(glue)

#Function to abbreviate dollar amounts and add symbol
covdata_comprss <- function(tx, label = FALSE) { 
  div <- findInterval(as.numeric(gsub("\\,", "", tx)), 
                      c(0, 1e3, 1e6, 1e9, 1e12) )  # modify this if negative numbers are possible
  if(label){
    paste(round( as.numeric(gsub("\\,","",tx))/10^(3*(div-1)), 0), 
          c("","K","M","B","T")[div], sep = "" )
  }
  else{
    paste(round( as.numeric(gsub("\\,","",tx))/10^(3*(div-1)), 1), 
          c("","K","M","B","T")[div], sep = "" )}
}


neighborhoods <- readRDS("neighborhoods.rds")

# CDBG Affrd. Housing Program
cdbg_assist <- readRDS("PY2014_present_CDBG_addresses.rds") |>
  st_as_sf(coords = c("lon", "lat"), crs = 4326) |>
  st_join(neighborhoods, join = st_within) |> 
  #filter(grepl("Latonia", NbhdLabel))|>
  mutate(Program = "CDBG Affordable Housing Repair")

google_map <- readRDS("covington_google_map_1.rds")

```


More than 130 times in the last 10 years, the City of Covington has helped vulnerable low-income homeowners – including the elderly, veterans, and those with disabilities – fix dangerous and unsafe conditions that could drive them from their homes.
 
In its current setup, the federally funded Homeowner Repair Program offers grants of up to $10,000 to fix owner-occupied, single-family homes in any area of Covington. 
 
Eligible repairs include certain electrical problems, plumbing issues (including broken water heaters and leaking pipes), HVAC problems (including carbon monoxide leaks and malfunctioning AC units/furnaces), roofs (plus gutters and downspouts), and accessibility modifications (like wheelchair ramps and handrails).
 
This map shows where grants have been awarded.
 
The homeowner is responsible for finding and selecting a contractor for a repair. City staff can assist by referring qualified contractors. Payment is made by the City directly to the contractor or repair person. 


```{r eval=TRUE, warning = FALSE, echo = FALSE, message = FALSE, fig.height=10, fig.width=10}


### CDBG loans awarded
cdbg_loans_granted <- cdbg_assist |>
  count(NbhdLabel, Program, name = "Loans/Grants Completed") |>
  st_drop_geometry() |>
  as.data.frame()

neigh_mappable <- neighborhoods %>%
  left_join(cdbg_loans_granted, by = "NbhdLabel") |>
  rename("geometry"="Shape",
         "Neighborhood"="NbhdLabel") |>
  select(Neighborhood, `Loans/Grants Completed`) |>
  filter(!is.na(`Loans/Grants Completed`)) |>
  mutate(Location = ifelse(grepl("South", Neighborhood), "South Covington", "North Covington"))


 neighborhood_labels <- labs(title = "\nHomeowner Repair Program",
       subtitle = "Grants Awarded, 2014-2023\n",
       caption = "\nCity of Covington\nNeighborhood Services | CovData | Google Maps",
       x = "", y = "")  
 

google_map <- readRDS("covington_google_map_1.rds")
cdbg_map <- google_map +  
  geom_sf(data = neigh_mappable, aes(fill = Neighborhood), alpha = 0.6,  inherit.aes = FALSE)+
  #scale_y_continuous(limits = c(min_lat, max_lat), expand = c(0, 0)) +
  #scale_x_continuous(limits = c(min_lon+0.2, max_lon+0.2), expand = c(0, 0)) +
  #scale_color_tq() +
  #covdata_fill_d("Set25") +
  #scale_fill_tq() +
  scale_fill_manual(values = c("dodgerblue2", "#E31A1C", "green4", "#6A3D9A", "#b35900",  "maroon", "gold1", "#00ffff", "#FB9A99", "palegreen2", "#CAB2D6", "#FDBF6F", "gray70", "khaki2",
            "maroon", "orchid1", "deeppink1", "blue1", "steelblue4", "darkturquoise", "green1",
            "yellow4", "yellow3", "darkorange4", "brown"))+
  geom_sf_text(data = neigh_mappable, aes(label = `Loans/Grants Completed`),
    size = 2.5,
    color = "black",
    inherit.aes = FALSE) +
  
 neighborhood_labels +
  theme_tq() +
  ggthemes::theme_map() + 
  theme(plot.title = element_text(size = 11, face = "bold"),
        legend.background = element_rect(linetype = "solid", colour = "black"),
        legend.position = c(0.01, 0.01),
        panel.border = element_rect(colour = "black", fill = NA, size = 0.3))
  


cdbg_map


```













