---
title: "Grants Helped 14 Neighborhoods"
author: ''
date: '2024-09-16'
slug: []
categories: []
tags:
  - Development
type: ''
subtitle: '$170K spread throughout The Cov'
image: ''
---

```{r setup, include=FALSE, echo = FALSE, warning = FALSE, message=FALSE}

library("tidyverse")
library("lubridate")
library("plotly")
library(readxl)
library(covdataplot)
library(magick)
library(extrafont)
library(sf)
library(ggmap)
library(gganimate)
library(gghighlight)
library(scales)
library(tidyquant)
library(glue)

#Function to abbreviate dollar amounts and add symbol
covdata_comprss <- function(tx, label = FALSE) { 
  div <- findInterval(as.numeric(gsub("\\,", "", tx)), 
                      c(0, 1e3, 1e6, 1e9, 1e12) )  # modify this if negative numbers are possible
  if(label){
    paste(round( as.numeric(gsub("\\,","",tx))/10^(3*(div-1)), 0), 
          c("","K","M","B","T")[div], sep = "" )
  }
  else{
    paste(round( as.numeric(gsub("\\,","",tx))/10^(3*(div-1)), 1), 
          c("","K","M","B","T")[div], sep = "" )}
}

dash_bld_permits <- readRDS("dash_bld_permits_for_google_maps.rds")
neighborhoods <- readRDS("neighborhoods.rds")
prj_list <- read.csv("project_list.csv", header = TRUE)
map_testing_this <- readRDS("north_covington_google_map.rds")

```


When neighborhoods have a plan and the desire to improve their communities, they turn to the City for financial help.

Covington leaders created the Neighborhood Grant Program in 2019 to enhance the physical appearance of small areas while enhancing the sense of social cohesion through shared projects.

Since then, the City has distributed about $170,000 for 37 projects in at least 14 neighborhoods (plus a cemetery/arboretum), including things like tree planting, flower pots, banners, dog-waste stations, festivals, water fountains, signs and benches.

This map shows the distribution of those grants by neighborhood.


```{r eval=TRUE, warning = FALSE, echo = FALSE, message = FALSE, fig.height=8, fig.width=10}


north_cov <- dash_bld_permits %>%
  filter(!(grepl("South Covington", Neighborhood)) & !is.na(Neighborhood))
pidn_map <- north_cov

lat_avg <- median(pidn_map$lat)- 0.02
lon_avg <- median(pidn_map$lon)- 0.008

max_lon <- max(pidn_map$lon)+ 0.001
min_lon <- min(pidn_map$lon)- 0.001

max_lat <- max(pidn_map$lat)+ 0.001
min_lat <- min(pidn_map$lat)- 0.001


neigh_mappable <- neighborhoods %>%
  left_join(prj_list, by = "NbhdLabel") |>
  select(Neigh_Grp, Grants) |>
  group_by(Neigh_Grp) |>
  summarize(Grants = sum(Grants)) |>
  filter(Grants > 0) |>
  mutate(Label = case_when(grepl("Riverside", Neigh_Grp) ~ "LR",
                           grepl("Old", Neigh_Grp) ~ "OT/MG",
                           grepl("Seminary", Neigh_Grp) ~ "SmSq",
                           .default = as.character(Neigh_Grp))) |>
  rename("geometry"="Shape",
         "Neighborhood"="Neigh_Grp")



 neighborhood_labels <- labs(title = "\nNeighborhood Grant Program",
       subtitle = "Projects Awarded, 2019-2023\n",
       caption = "\nCity of Covington\nNeighborhood Services | CovData | Google Maps",
       x = "", y = "")  



map_test <- map_testing_this +
  geom_sf(data = neigh_mappable, aes(fill = Neighborhood), alpha = 0.6,  inherit.aes = FALSE, show.legend = TRUE)+
  scale_y_continuous(limits = c(min_lat, max_lat), expand = c(0, 0)) +
  #scale_x_continuous(limits = c(min_lon, max_lon), expand = c(0, 0)) +
  #scale_color_tq() +
  #covdata_fill_d("Set25") +
  #scale_fill_tq() +
  scale_fill_manual(values = c("dodgerblue2", "#E31A1C", "green4", "#6A3D9A", "#b35900",  "maroon", "gold1", "darkblue", "#FB9A99", "palegreen2", "#CAB2D6", "#FDBF6F", "gray70", "khaki2",
            "maroon", "orchid1", "deeppink1", "blue1", "steelblue4", "darkturquoise", "green1",
            "yellow4", "yellow3", "darkorange4", "brown"))+
  geom_sf_text(data = neigh_mappable, aes(label = Grants),
    size = 3.0,
    color = "black",
    inherit.aes = FALSE)+
  
 neighborhood_labels +
  theme_tq() 


map_test





```