---
title: "In the Cov, employees steadily returning to the office"
author: ''
date: '2025-03-05'
slug: []
categories: []
tags:
  - Development
type: ''
subtitle: ''
image: ''
---


```{r setup, include=FALSE, echo = FALSE, warning = FALSE, message=FALSE}

library("tidyverse")
library("lubridate")
library("plotly")
library(readxl)
library(covdataplot)
library(magick)
library(extrafont)
library(sf)
library(ggmap)
library(gganimate)
library(gghighlight)
library(scales)
library(tidyquant)
library(glue)
library(widyr)
library(tidytext)
library(ggimage)


employees <- read.csv("employee_visits_6a_6p_weekdays_150min.csv", header = TRUE) 


```

During the onset of the Covid-19 pandemic in 2020, many workplaces utilized work-from-home strategies as a way to protect employees from an infectious virus about which little was known. 
 
In the immediate years since, the work-from-home philosophy lingered. Little by little, however, at least in Covington, the number of employees in the workplace continue to rise, though not yet to pre-pandemic levels.
 
The chart above shows the year-by-year average of daily foot traffic from Placer.ai software tied to “work locations,” not only downtown but around the city.


```{r eval=TRUE, warning = FALSE, echo = FALSE, message = FALSE, fig.width = 10, fig.height = 6}


## display daily average
plot_labels_a <-  labs(x = "\nDate", 
       y = "Employee Visits\n", 
       title = "Daily Average Employee Foot Traffic in Covington",
       subtitle = "Visits between 6am and 6pm, Monday-Friday for at least 150 minutes\n",
       caption = "\nAdministration\nCity of Covington\nSource: Placer.ai | CovData | 2025")
  
employee_visits <- employees |>
  mutate_at(vars(date), list(mdy)) |>
  mutate(Period = case_when(between(date, as.Date('2017-01-01'), as.Date("2020-03-15"))~"Before COVID",
                            between(date, as.Date('2020-03-16'), as.Date("2021-06-10"))~"COVID Restrictions",
                            between(date, as.Date('2021-06-11'), as.Date("2025-01-31"))~"COVID Restrictions Ended"))

employee_visit_count <- employee_visits |>
  mutate(year = as.character(year(date))) |>
  filter(employees > 0, !year %in% 2025) |>
  count(year, Period, wt = mean(employees), name = "Employee Visits") |>
  ggplot(aes(year, `Employee Visits`, fill = Period))+
  geom_bar(stat = 'identity', position = "dodge")+
  #bar_plot_labels +
  scale_fill_manual(values = c("#0047ba", "#D73027", "#33A02C")) +
  #covdata_fill_d("Paired")+
  scale_y_continuous(limits = c(0, 30000),
                     label=scales::label_number_si(),
                     expand = expansion(mult = c(0, .1)))+
  
  geom_text(aes(label = scales::comma(`Employee Visits`)), vjust = -0.5, position = position_dodge(0.9),
            size = 3.5)+
  plot_labels_a +
  
  theme_tq() +
  theme(panel.grid.major.x = element_line(color = "white",
                                          size = 0,
                                          linetype = 2))
  #facet_wrap(~ZONE_ID)

covdata_plot(employee_visit_count, "cov.logo.blue")



```

