---
title: CovConnect Data Trends
author: ''
date: '2023-03-13'
slug: []
categories: []
tags:
  - CovConnect
  - Wi-Fi
type: ''
subtitle: 'Dec. 2020 - March 2023'
image: ''
---

Covington Connect is an aggressive effort to smash the digital divide in Covington by expanding access to free public Wi-Fi throughout much of the City.

In a [previous post](https://covanalytics.github.io/post/2022-08-22-covconnect-registrations/), we outlined the purpose, partners, and phases of the Covington Connect project.  This post briefly looks at the data trends of Wi-Fi users, specifically how much data has been downloaded and uploaded by student and non-student users since December 2020.

A download pulls data from the internet to the users computer (watching a video; opening a webpage, etc.) and an upload takes data from the users computer and puts it on the internet (sending an email; uploading a homework assignment, etc.)

The graph below shows these data trends in Terabytes (TB), a large unit of digital data.  Since December 2020, 125.62 TB of data has been transferred (downloads and uploads) over the Covington Connect Wi-Fi system. Student users have downloaded 50.51 TB and uploaded 4.41 TB.  Non-student users have downloaded 64.39 TB and uploaded 6.31 TB. 

For a point of reference, is has been estimated that 10 TB could hold the entire printed collection of the U.S. Library of Congress, while a single TB could hold 1,000 copies of the Encyclopedia Brittanica.^[https://www.teradata.com/Glossary/What-is-a-Terabyte]


```{r setup, include=FALSE, echo = FALSE}
library("tidyverse")
library("lubridate")
library("plotly")
library(readxl)
library(covdataplot)
library(magick)
library(extrafont)



dt_cvcnt <- read_excel("U:/data_downloads_uploads.xlsx", col_names = TRUE)%>%
  as.data.frame()

```

```{r eval=TRUE, echo = FALSE}
labels <- labs(x = "Data Trend", 
               y = "Type\n", 
               title = "Covington Connect Wi-Fi",
               subtitle = "Data Trends Among Users (Dec. 2020 - March 2023)\n",
               caption = "Administration\nCity of Covington\n2023 | CovData")


dt_plot <- dt_cvcnt %>%

  ggplot(aes(x = Type, y = Data, fill = Type))+
  geom_bar(stat = 'identity', position = "dodge", show.legend = FALSE) +
  covdata_fill_d("Pantones")+
  scale_y_continuous(limits = c(0,100),
                     expand = expansion(mult = c(0, .1)))+
  geom_text(aes(label=Label) ,hjust = 0.5, vjust = -1.0,  size = 3.0)+
  facet_wrap(~ User)+
  
  labels +
  covdata_theme()
          

covdata_plot(dt_plot, "cov.logo.blue", save_name = "cov_data_trends")

```



Go to the [Covington Connect](https://www.covingtonky.gov/government/covington-connect) page on the City's website for more information.\
