---
title: "BLINK foot traffic more than doubled '24 high"
author: ''
date: '2024-10-25'
slug: []
categories: []
tags:
  - Development
type: ''
subtitle: ''
image: ''
---

```{r setup, include=FALSE, echo = FALSE, warning = FALSE, message=FALSE}

library("tidyverse")
library("lubridate")
library("plotly")
library(readxl)
library(covdataplot)
library(magick)
library(extrafont)
library(sf)
library(ggmap)
library(gganimate)
library(gghighlight)
library(scales)
library(tidyquant)
library(glue)

#Function to abbreviate dollar amounts and add symbol
covdata_comprss <- function(tx, label = FALSE) { 
  div <- findInterval(as.numeric(gsub("\\,", "", tx)), 
                      c(0, 1e3, 1e6, 1e9, 1e12) )  # modify this if negative numbers are possible
  if(label){
    paste(round( as.numeric(gsub("\\,","",tx))/10^(3*(div-1)), 0), 
          c("","K","M","B","T")[div], sep = "" )
  }
  else{
    paste(round( as.numeric(gsub("\\,","",tx))/10^(3*(div-1)), 1), 
          c("","K","M","B","T")[div], sep = "" )}
}

blink24 <- readRDS("blink_zone_visits.rds") 

```

If downtown Covington seemed crowded last weekend during the four-day BLINK outdoor light and art event, it was. Very crowded. Especially compared to every other evening of 2024.
 
This chart shows peak foot traffic night by night during the event, as compared to every other evening in 2024, in the area where the BLINK installations were featured. The peak night – Saturday – is more than double the two previous highs during the year, which we think came during St. Patrick’s Day weekend festivities in mid-March and the Labor Day riverfront fireworks show in early September.
 
The number does not represent all people who were downtown at any given moment – only those with cell phones turned on and who were moving around (i.e. not residents or downtown employees) during the hours of 7 p.m. to midnight.
 
The Placer.ai software leverages data and algorithms to estimate visits. The data aggregated by Placer.ai is obtained from hundreds of partner mobile apps (that collect data from mobile devices).


```{r eval=TRUE, warning = FALSE, echo = FALSE, message = FALSE, fig.width = 8, fig.height = 6}


#////////////////////////////////////////////////////////////
### BLINK 2024

 #specifying labels  
plot_labels <-  labs(x = "\n2024\n", 
       y = "Visits", 
       title = "Daily Foot Traffic in BLINK 2024 Zone",
       subtitle = "Visits between 7pm and 11:59pm\n",
       caption = "Administration\nCity of Covington\nSource: Placer.ai | CovData | 2024")
  


#blink visits
blink_plot24 <- blink24 %>%
  mutate_at(vars(date), list(mdy))%>%
  #mutate(`M-Y` = format(Date, "%m-%Y"))%>%
  ggplot(aes(x=date, y=visits, fill = event, width = 0.99999))+
  #geom_line(lwd = 0.8) + 
  geom_bar(stat = "identity", show.legend = FALSE) + 
  #geom_rect(aes(xmin = ymd("2022-10-13"), xmax = ymd("2022-10-16"), 
  #              ymin = -Inf, ymax = Inf), alpha = 0.01, fill = "#00c1de", colour = NA)+

  geom_label(aes(x = ymd("2024-08-28"), y = 14000, label = "BLINK 2024\nOct.17 - Oct.20\n48.43k visitors"), 
             hjust = 0.5, 
             vjust = 0.5, 
             lineheight = 0.8,  
             color = "black", 
             #fill = "#c8ff1f",
             fill = "#00c1de", 
             label.size = 0.2, 
             family="Franklin Gothic Medium", 
             size = 3) +
  geom_curve(aes(x = ymd("2024-09-03"), y = 12790, xend = ymd("2024-10-13"), yend = 12000), 
                           colour = "#000000", 
                           curvature = 0.2,
                           size=0.7,
             arrow = arrow(angle = 30, length=unit(0.1, "in"), type="closed")) +
                          #arrow = arrow(length = unit(0.03, "npc")))+
   
  #geom_area(fill = "red")+
  
  #geom_point(size = 1) +
  scale_x_date(breaks = seq(ym("2024-01"), ym("2025-01"), by = "1 month"), date_labels = "%b" )+
  scale_y_continuous(limits = c(0, 19000),
                     labels = scales::label_number_si(), n.breaks = 16,
                     expand = expansion(mult = c(0, .1))) +
  plot_labels+
  scale_fill_manual(values = c("#878787", "#00c1de")) +
  theme_tq() 
 
  #covdata_theme(plot.background.fill = "covington.light.gray")


covdata_plot(blink_plot24, "cov.logo.blue")





```