---
title: Current Revenues and Expenses
author: ''
date: '2022-12-09'
slug: []
categories: []
tags:
  - Finance
type: ''
subtitle: 'Annual Comprehensive Financial Report, 2004-2021'
image: ''
---


Each year, the City of Covington is required by State law to publish an Annual Comprehensive Financial Report (ACFR) in cooperation with an independent firm of licensed certified public accounts. The ACFR is intended to provide informative and relevant financial data to the residents of the City, the City Commission, investors, creditors and any other interested reader. It includes all statements and disclosures necessary for the reader to obtain a thorough understanding of the City’s financial activities. 

The ACFRs are available on the [Finance Department page](https://www.covingtonky.gov/government/departments/finance) and are being archived on the [CovData Repository](http://data.covingtonky.gov/Repository/)

The graph below shows current revenues and current expenses from the Statement of Revenues, Expenditures and Changes in Fund Balances for all government funds by fiscal year.  

**The graph shows only current expenses; therefore it does not include expenses related to debt service and capital outlay**



```{r setup, include=FALSE, echo = FALSE}
library("tidyverse")
library("lubridate")
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

#Function to abbreviate dollar amounts and add symbol
covdata_comprss <- function(tx, label = FALSE) { 
      div <- findInterval(as.numeric(gsub("\\,", "", tx)), 
         c(0, 1e3, 1e6, 1e9, 1e12) )  # modify this if negative numbers are possible
      if(label){
        paste(round( as.numeric(gsub("\\,","",tx))/10^(3*(div-1)), 0), 
           c("","K","M","B","T")[div], sep = "" )
      }
      else{
        paste(round( as.numeric(gsub("\\,","",tx))/10^(3*(div-1)), 1), 
           c("","K","M","B","T")[div], sep = "" )}
      }


#Load Audited Revenues and Expenses from ACFRs
rev_exp <- readRDS("rev_exp.rds")

rev_exp_longer <- rev_exp %>%
  pivot_longer(!FY, names_to = "Type", values_to = "Amount")%>%
  mutate(Amount_ = formatC(Amount, format = "d", big.mark = ","),
         `Fiscal Year` = substr(FY, start = 3, stop = 4),
         Value = covdata_comprss(Amount, label = TRUE))


```



```{r eval=TRUE}

# Current revenue / expenses plot

acfr_plot <- rev_exp_longer %>%
  
ggplot(aes(x=`Fiscal Year`, y = Amount, fill = Type, label = Amount_))+
  geom_bar(stat = 'identity', position = "dodge")+
  
  theme_bw()+
  scale_discrete_manual("fill", values = c('#52BE80', '#EC7063'), breaks=c("Revenue", "Expense"))+
  #scale_fill_manual(values=c('#A946D2','#D26346'), name = "")+
  #scale_x_continuous(breaks=rev_exp$FY)+
  scale_y_continuous(label=scales::label_number_si(),
                     expand = expansion(mult = c(0, .1)))+
  geom_text(aes(label=Value),vjust=-0.5, position = position_dodge(0.9), size = 2.3)+
  labs(subtitle = "Current Revenues & Expenses by Fiscal Year", caption = "Source: Covington Finance Department\nDebt service and capital outlay not included")+
  
  
  theme(legend.position = "right",
        legend.title = element_blank(),
        axis.title = element_blank(),
        panel.grid.major = element_line(colour = "#D4D2D3"),
        plot.caption = element_text(hjust = 0, face = "italic", size = 10),
        text = element_text(size = 13))

#ggsave("revenue-expenses.jpg", acfr_plot, width = 800, height = 400, units = "px", dpi = 120)

acfr_plot



```

Go to the [Revenues & Expenses](http://data.covingtonky.gov/Dashboards/Revenues_Expenses/) dashboard for an updated graphic with the completion of each new ACFR.







