---
title: "Who Recycles?"
author: ''
date: '2024-08-06'
slug: []
categories: []
tags: 
  - Recycling
type: ''
subtitle: Percentage of households that participate has increased in every neighborhood
image: ''
---

```{r setup, include=FALSE, echo = FALSE}

library("tidyverse")
library("lubridate")
library("plotly")
library(readxl)
library(covdataplot)
library(magick)
library(extrafont)
library(sf)
library(ggmap)
library(gganimate)
library(gghighlight)
library(scales)
library(tidyquant)
library(glue)

#Function to abbreviate dollar amounts and add symbol
covdata_comprss <- function(tx, label = FALSE) { 
  div <- findInterval(as.numeric(gsub("\\,", "", tx)), 
                      c(0, 1e3, 1e6, 1e9, 1e12) )  # modify this if negative numbers are possible
  if(label){
    paste(round( as.numeric(gsub("\\,","",tx))/10^(3*(div-1)), 0), 
          c("","K","M","B","T")[div], sep = "" )
  }
  else{
    paste(round( as.numeric(gsub("\\,","",tx))/10^(3*(div-1)), 1), 
          c("","K","M","B","T")[div], sep = "" )}
}




```


The number of households that participate in the Covington curbside recycling program has grown tremendously in the last eight years.
 
Here are the numbers by neighborhood. Numbers represent the percentage of households who contract for trash pickup that also use a recycling cart. Notice that every single neighborhood has increased over this period.
 
The recycling program carries no additional cost beyond the annual trash collection fee. 
 
In all, some 2,410 tons of recyclable material was diverted from landfills in Fiscal Year 2024.
 
For information on recycling in The Cov, how to sign up, and what can be recycled in the curbside carts, see [Recycling Guidelines](https://www.covingtonky.gov/government/departments/neighborhood-services/solid-waste-recycling/recycling-guidelines).





```{r eval=TRUE, warning = FALSE, echo = FALSE, message = FALSE, fig.height=6, fig.width=7}

recy <- readRDS("recycling_accounts.rds")

recy_neigh <- recy |>
  mutate(Date = ymd(Date),
         date_month = month(Date, label = TRUE, abbr = FALSE),
         Year = as.character(Year)) |>
  filter(Year %in% c("2016", "2024"), date_month %in% ("June"), !Neighborhood %in% "Not Recorded")|>
  select(Year, Neighborhood, PCT_RECYCLING) |>
  mutate(PCT_RECYCLING = round(PCT_RECYCLING, 0)) |>
  pivot_wider(names_from = Year, values_from = PCT_RECYCLING) |>
  #bind_rows(total_recy) |>
  rename(c("percent_2016"="2016", "percent_2024"="2024")) |>
  mutate(bump_2016 = case_when(percent_2016 < percent_2024 ~
                                   percent_2016 - 4,
                                 percent_2016 > percent_2024 ~
                                   percent_2016 + 4,
                                 TRUE ~ NA_real_),
         bump_2024 = case_when(percent_2016 < percent_2024 ~
                                    percent_2024 + 4,
                                  percent_2016 > percent_2024 ~
                                    percent_2024 - 4,
                                  TRUE ~ percent_2024 + 4))
recy_neigh <- recy_neigh |>         
  mutate(y_position = rev(1:23))


arrows_data <- recy_neigh %>%
  filter(abs(percent_2016 - percent_2024) > 1) %>%
  mutate(midpoint = (percent_2016 + 2*percent_2024)/3) %>%
  select(Neighborhood, y_position, percent_2016, midpoint) %>%
  pivot_longer(c(percent_2016, midpoint), names_to="type", values_to="x")


plot_labels <-  labs(x = "Percent", 
       y = "", 
       title = "Increase in Recycling Participation",
       subtitle = "Change by Neighborhood from June 2016 to June 2024 \n",
       caption = "Neighborhood Services\nCity of Covington\nSource: Rumpke | CovData | 2024")


recy_change <- recy_neigh |>
  pivot_longer(cols = -c(Neighborhood, y_position),
               names_to=c(".value", "year"),
               names_sep = "_") %>%
  drop_na() %>%
  ggplot(aes(x=percent, y=Neighborhood, color=year,  group=Neighborhood)) +
  #geom_ribbon(data = strip_data,
  #            aes(x = x, ymin=ymin, ymax = ymax, group=y_position, fill=fill),
  #            inherit.aes = FALSE) +
  geom_line(color="#e6e6e6", linewidth=1.75, show.legend = FALSE) +
  geom_path(data=arrows_data, aes(x=x, y=Neighborhood, group=Neighborhood),
            color="red", 
            linewidth = 0.69,
            arrow = arrow(angle = 30, length=unit(0.1, "in"), type="closed"),
            show.legend = FALSE,
            inherit.aes = FALSE) +
  geom_point(size=2, show.legend = TRUE, ) +
  geom_text(aes(label=glue("{percent}%"), x=bump),
            size=3,
            show.legend = FALSE) +
  scale_color_manual(name="Year",
                     breaks=c("2016", "2024"),
                     values=c("#727272", "#0047ba"),
                     labels=c("2016", "2024")) +
  scale_x_continuous(breaks = c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100), limits = c(0, 100))+
  
  scale_fill_tq() +
  covdata_theme() +
  theme_tq()+
  plot_labels +
  

  theme(
    legend.title = element_text(),
    legend.position = "bottom",
    legend.justification = "center",
    plot.title.position = "plot",
    axis.ticks.y = element_line(color = c(rep(NA, nrow(recy_neigh)),
                                          rep("darkgray", nrow(recy_neigh)+1)),
                                size=0.2)
  )

  #theme_tq() 
 

covdata_plot(recy_change, "cov.logo.blue")
  



```













