---
title: "Revenue 'Furnace'"
author: ''
date: '2024-08-16'
slug: []
categories: []
tags:
  - Finance
  - Development
type: ''
subtitle: 'Downtown glows red in a tax revenue heat map'
image: ''
---


```{r setup, include=FALSE, echo = FALSE, warning = FALSE, message=FALSE}

library("tidyverse")
library("lubridate")
library("plotly")
library(readxl)
library(covdataplot)
library(magick)
library(extrafont)
library(sf)
library(ggmap)
library(gganimate)
library(gghighlight)
library(scales)
library(tidyquant)
library(glue)

#Function to abbreviate dollar amounts and add symbol
covdata_comprss <- function(tx, label = FALSE) { 
  div <- findInterval(as.numeric(gsub("\\,", "", tx)), 
                      c(0, 1e3, 1e6, 1e9, 1e12) )  # modify this if negative numbers are possible
  if(label){
    paste(round( as.numeric(gsub("\\,","",tx))/10^(3*(div-1)), 0), 
          c("","K","M","B","T")[div], sep = "" )
  }
  else{
    paste(round( as.numeric(gsub("\\,","",tx))/10^(3*(div-1)), 1), 
          c("","K","M","B","T")[div], sep = "" )}
}




```


Just under 60 percent of the tax revenue generated in Covington for the City’s General Fund comes from occupational license revenue (which includes both the payroll tax and net profit tax). 
 
The General Fund is the operations fund used to pay the salaries of employees who deliver most City services – such as Police, EMS, Fire, Public Works, and Parks & Rec.
 
This heat map shows where that revenue was generated in calendar year 2023.


```{r eval=TRUE, warning = FALSE, echo = FALSE, message = FALSE, fig.height=9, fig.width=9}


  
city <- readRDS("city_boundary.rds")
cov_city <- st_transform(city, crs = 4326)


p_tax_heat <- st_read("payroll_np_amounts_2023_heat_surface.shp", quiet = TRUE)|>
  filter(gridcode != 1) |>
  dplyr::rename(Amount = gridcode) 
p_tax_heat_sf <- st_transform(p_tax_heat, crs = 4326)


tax_labels <- labs(title = "Payroll Tax and Net Profit Tax Revenue, 2023",
                         subtitle = "Heat Map\n",
                         caption = "Finance\nCity of Covington\n GoogleMaps | CovData | 2024",
                         x = "", y = "") 

prop_tax_map_plot <-  readRDS("cov_map_bw.RDS")  + ggthemes::theme_map() +
  geom_sf(data = p_tax_heat_sf, aes(fill = Amount), colour = NA, alpha=0.50, inherit.aes = FALSE)+
  #scale_fill_viridis(option = "magma", direction = -1) +
  covdata_fill_c("Spectral", reverse = TRUE) +
  geom_sf(data = cov_city, fill = NA, lwd = 0.8, color = "black", inherit.aes = FALSE)+
  #scale_color_tq() +
  #scale_fill_tq() +
  tax_labels +
  #covdata_theme() +
  theme(title = element_text(size = 12),
        legend.text = element_blank(),
        legend.title = element_text(size = 8),
        axis.ticks = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank())


prop_tax_map_plot





```










